additional3D

### 2021-06-17 additional.Rmd
code to simplify and merge

df_sec <- read.csv("df_secondary.csv",sep=",")
exclet <- names(df_sec) %in% c("run", "density","step")

df_sec <- df_sec[!exclet] %>% group_by(ID,RND,eth_con_loc,eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)

@@

@@

```{r asym_baseline, fig.cap="Fig. 8 orig", echo = FALSE}

@@

df <- df %>% filter(df$dominant <= 15) 
df <- df %>% filter(df$fraction_blue==50|df$fraction_blue==60|df$fraction_blue==80)

@@

@@

@@

```{r by-product_cons_original, fig.cap="Effect of liberals majority vs minority on value segregation conservatives", echo = FALSE}

@@

ggsave("lib_cons.jpg",plot=lib_cons)

@@

@@

lib_cons_et <- ggpubr::ggarrange(cons_maj_et,cons_min_et, common.legend = TRUE, legend = "bottom")

#ggsave("lib_cons.jpg",plot=lib_cons)

@@

```{r beta_maj, fig.cap="effect liberals one  dataset", echo = FALSE}

#####
# Ethnic and value of liberals above each other
mech_vlmj <- mech %>% filter(fraction_blue == 50 | fraction_blue == 80) %>%  filter(val_lib_min==0 | val_lib_min==1 |val_lib_min==7) %>% gather(key = segregation, value = Clustmj, de_cl_bl, dv_cl_bl)

librmj <- ggplot(data=mech_vlmj,aes(x=val_lib_loc,y = Clustmj,shape=`segregation`,linetype=as.factor(fraction_blue))) + 
  geom_point(size=1.5,color="blue") + geom_line(color="blue") +
facet_wrap(~val_lib_min,dir="v",labeller=labeller(val_lib_min=valueminority.labs)) +
  xlab("ß value liberals majority") + ylab("Spatial Clustering") +
  scale_y_continuous(breaks= seq(0,2,by=0.25)) +
  scale_linetype_manual(values=c("solid","dashed"),labels=c("50%","80%"),name="% Majority" ) +
  scale_shape_manual(values=c("square","circle"),labels=c("Ethnic","Value"),name="Segregation" ) +
 ggtitle("Liberals Majority") +
    geom_hline(yintercept=1,color="red") +
      theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

ggsave("lib_lib.jpg",plot=lib_lib)

@@

```{r etlib_min, fig.cap="Ethnic preference majority or minority over liberals or conservatives minority", echo = FALSE}

excl <- names(df_etlib) %in% c("run", "density","step")
df_etlib <- df_etlib[!excl] %>% group_by(ID,eth_con_loc,eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)

## Majority

df_ethloc <- df_etlib %>% filter(ID == "etlib_loc") %>% filter(fraction_blue == 80) %>% gather(key = subgroup, value = Clustetmj, de_sq_or,dv_sq_or,de_cl_or,dv_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_or","de_cl_or"), "Value" = c("dv_sq_or","dv_cl_or") ),"Ethnic"),
              `orientation` = fct_relevel(fct_collapse(subgroup,"Conservative" = c("de_sq_or","dv_sq_or"), "Liberal" = c("de_cl_or","dv_cl_or")), "Conservative"))

maj_min <- ggplot(data=df_ethloc,aes(x=eth_lib_loc,y = Clustetmj,linetype=`segregation`,shape = `orientation`)) + 
  geom_point(size=1.5,color="orange") + geom_line(color="orange") +
facet_wrap(~eth_lib_min,dir="v",labeller=labeller(eth_lib_min=ethnicminority.labs)) +
  xlab("ß ethnic liberals majority") + ylab("Spatial Clustering") +
  scale_y_continuous(breaks= seq(0,5,by=0.50)) +
  scale_linetype_manual(values=c("solid","dashed"),labels=c("Ethnic","Value"),name="Segregation" ) +
  scale_shape_manual(values=c("square","circle"),labels=c("Conservative","Liberal"),name="Orientation \n minority" ) +
 ggtitle("") +
    geom_hline(yintercept=1,color="red") +
      theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

ggplotly(maj_min)
   maj_min
## Minority

df_ethmin <- df_etlib %>% filter(ID == "etlib_min") %>% filter(fraction_blue == 80) %>% gather(key = subgroup, value = Clustetmn, de_sq_or,dv_sq_or,de_cl_or,dv_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_or","de_cl_or"), "Value" = c("dv_sq_or","dv_cl_or") ),"Ethnic"),
              `orientation` = fct_relevel(fct_collapse(subgroup,"Conservative" = c("de_sq_or","dv_sq_or"), "Liberal" = c("de_cl_or","dv_cl_or")), "Conservative"))

min_min <- ggplot(data=df_ethmin,aes(x=eth_lib_min,y = Clustetmn,linetype=`segregation`,shape = `orientation`)) + 
  geom_point(size=1.5,color="orange") + geom_line(color="orange") +
facet_wrap(~eth_lib_loc,dir="v",labeller=labeller(eth_lib_loc=ethnicmajority.labs)) +
  xlab("ß ethnic liberals minority") + ylab("Spatial Clustering") +
  scale_y_continuous(breaks= seq(0,5,by=0.50)) +
  scale_linetype_manual(values=c("solid","dashed"),labels=c("Ethnic","Value"),name="Segregation" ) +
  scale_shape_manual(values=c("square","circle"),labels=c("Conservative","Liberal"),name="Orientation \n minority" ) +
 ggtitle("") +
    geom_hline(yintercept=1,color="red") +
      theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

ggplotly(min_min)
   min_min

eth_lib_min <- ggpubr::ggarrange(maj_min,min_min, common.legend = TRUE, legend = "bottom")

ggsave("eth_lib_min.jpg",plot=eth_lib_min)

```{r etlib_min_test fraction, fig.cap="Ethnic preference majority or minority over liberals or conservatives minority", echo = FALSE}

df_etlib <- read.csv("df_etlib.csv",sep=",")

excl <- names(df_etlib) %in% c("run", "density","step")
df_etlib <- df_etlib[!excl] %>% group_by(ID,eth_con_loc,eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)

## Majority

>>>>

df_sec <- read.csv("df_secondary.csv",sep=",")
exclet <- names(df_sec) %in% c("run", "density","step")
df_sec <- df_sec[!exclet] %>% group_by(ID,RND,eth_con_loc,eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)

@@

df_etlib <- read.csv("df_etlib_all.csv",sep=",")
excl <- names(df_etlib) %in% c("run", "density","step")
df_etlib <- df_etlib[!excl] %>% group_by(ID,eth_con_loc,eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)

df_3Do <- read.csv("3D_old.csv",sep=",")
excl3D <- names(df_3Do) %in% c("run", "density","step")
df_3Do <- df_3Do[!excl3D] %>% group_by(eth_con_loc, eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)

@@

# Between the 2 baseline: decide!
```{r asym_baseline, fig.cap="Fig. 8 orig", echo = FALSE}
# Effect of ethnic asymmetry: all beta dominant equal

@@

# df <- df %>% filter(df$dominant <= 15) 
# df <- df %>% filter(df$fraction_blue==50|df$fraction_blue==60|df$fraction_blue==80)

@@

# Sensitivity to value liberal locals , while the others are keep 20

@@

majcons <-  ggplot(data = df) + geom_point(aes(x=dominant,y=dv_sq_bl, colour = vl_sq_bl),shape = "circle")  + geom_line(aes(x=dominant,y=dv_sq_bl, linetype = as.factor(fraction_blue))) +
           geom_point(aes(x=dominant,y=de_sq_bl, colour = et_sq_bl),shape="square") + geom_line(aes(x=dominant,y=de_sq_bl, linetype = as.factor(fraction_blue)))+ ggtitle("majcons")

majlib <-  ggplot(data = df) + geom_point(aes(x=dominant,y=dv_cl_bl, colour = vl_cl_bl),shape = "circle")  + geom_line(aes(x=dominant,y=dv_cl_bl, linetype = as.factor(fraction_blue))) +
           geom_point(aes(x=dominant,y=de_cl_bl, colour = et_cl_bl),shape="square") + geom_line(aes(x=dominant,y=de_cl_bl, linetype = as.factor(fraction_blue))) + ggtitle("majlib")

mincons <-  ggplot(data = df) + geom_point(aes(x=dominant,y=dv_sq_or, colour = vl_sq_or),shape = "circle")  + geom_line(aes(x=dominant,y=dv_sq_or, linetype = as.factor(fraction_blue))) +
           geom_point(aes(x=dominant,y=de_sq_or, colour = et_sq_or),shape="square") + geom_line(aes(x=dominant,y=de_sq_or, linetype = as.factor(fraction_blue))) + ggtitle("mincons")

minlib <-  ggplot(data = df) + geom_point(aes(x=dominant,y=dv_cl_or, colour = vl_cl_or),shape = "circle")  + geom_line(aes(x=dominant,y=dv_cl_or, linetype = as.factor(fraction_blue))) +
           geom_point(aes(x=dominant,y=de_cl_or, colour = et_cl_or),shape="square") + geom_line(aes(x=dominant,y=de_cl_or, linetype = as.factor(fraction_blue)))+ ggtitle("minlib")

@@

```{r by-product_cons_original, fig.cap="Effect of liberals majority vs minority on value segregation conservatives", echo = FALSE}
# It goes
# ethnic and value segregation for each group in the annex

@@

# ggsave("lib_cons.jpg",plot=lib_cons)
ggpubr::annotate_figure(lib_cons,
               top = "Effect of liberals majority vs minority on value segregation conservatives")
```

```{r beta_maj, fig.cap="effect liberals one  dataset", echo = FALSE}
# It goes
#####
# Ethnic and value of liberals above each other
mech_vlmj <- mech %>% filter(fraction_blue == 50 | fraction_blue == 80) %>%  filter(val_lib_min==0 | val_lib_min==1 |val_lib_min==7) %>% gather(key = segregation, value = Clustmj, de_cl_bl, dv_cl_bl)

librmj <- ggplot(data=mech_vlmj,aes(x=val_lib_loc,y = Clustmj,shape=`segregation`,linetype=as.factor(fraction_blue))) + 
  geom_point(size=1.5,color="blue") + geom_line(color="blue") +
facet_wrap(~val_lib_min,dir="v",labeller=labeller(val_lib_min=valueminority.labs)) +
  xlab("ß value liberals majority") + ylab("Spatial Clustering") +
  scale_y_continuous(breaks= seq(0,2,by=0.25)) +
  scale_linetype_manual(values=c("solid","dashed"),labels=c("50%","80%"),name="% Majority" ) +
  scale_shape_manual(values=c("square","circle"),labels=c("Ethnic","Value"),name="Segregation" ) +
 ggtitle("Liberals Majority") +
    geom_hline(yintercept=1,color="red") +
  guides(color = "black") +
      theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

lib_lib
# ggsave("lib_lib.jpg",plot=lib_lib)

@@

```{r 3D_table, fig.cap="Each grouptype, distribution liberals faceted by ethnic ratio", echo = FALSE}

df_fin <- df_3D %>% mutate(RND = case_when(
  val_lib_loc==5 & val_lib_min==5 & eth_con_loc == 5 & eth_con_min == 5 ~ "H",
  val_lib_loc==20 & val_lib_min==20 & eth_con_loc == 20 & eth_con_min == 20 ~ "L"
))

cmj <- subset(df_fin, eth_lib_loc ==0 & eth_lib_min == 0) %>% gather(subgroup, Segra, de_sq_bl,dv_sq_bl) %>% ggplot(aes(x=circle_orange,y=Segra,shape = subgroup, color = RND)) + geom_point() + geom_line() +
  scale_color_manual(values = c("green","purple"),labels = c("high","low"), guide = guide_legend(title = "Randomness")) + 
  scale_shape_manual(values = c("square","circle"),labels = c("ethnic","Value"), guide = guide_legend(title = "Segregation")) + 
 scale_x_discrete(limits = seq(10,90 ,by = 10)) +
  facet_wrap(~ fraction_blue, nrow = 1) +
  ggtitle("Conservative majority") +
  theme_bw()

lb <- subset(df_fin, eth_lib_loc ==0 & eth_lib_min == 0) %>% gather(subgroup, Segra, de_cl_bl,dv_cl_bl) %>% ggplot(aes(x=circle_orange,y=Segra,shape = subgroup, color = RND)) + geom_point() + geom_line() +
  scale_color_manual(values = c("green","purple"),labels = c("high","low"), guide = guide_legend(title = "Randomness")) + 
  scale_shape_manual(values = c("square","circle"),labels = c("ethnic","Value"), guide = guide_legend(title = "Segregation")) + 
 scale_x_discrete(limits = seq(10,90 ,by = 10)) +
  facet_wrap(~ fraction_blue, nrow = 1) +
  ggtitle("Liberals majority") +
  theme_bw()

cm <- subset(df_fin, eth_lib_loc ==0 & eth_lib_min == 0) %>% gather(subgroup, Segra, de_sq_or,dv_sq_or) %>% ggplot(aes(x=circle_orange,y=Segra,shape = subgroup, color = RND)) + geom_point() + geom_line() +
  scale_color_manual(values = c("green","purple"),labels = c("high","low"), guide = guide_legend(title = "Randomness")) + 
  scale_shape_manual(values = c("square","circle"),labels = c("ethnic","Value"), guide = guide_legend(title = "Segregation")) + 
 scale_x_discrete(limits = seq(10,90 ,by = 10)) +
  facet_wrap(~ fraction_blue, nrow = 1) +
  ggtitle("Conservative minority") +
  theme_bw()

lm <- subset(df_fin, eth_lib_loc ==0 & eth_lib_min == 0) %>% gather(subgroup, Segra, de_cl_or,dv_cl_or) %>% ggplot(aes(x=circle_orange,y=Segra,shape = subgroup, color = RND)) + geom_point() + geom_line() +
  scale_color_manual(values = c("green","purple"),labels = c("high","low"), guide = guide_legend(title = "Randomness")) + 
  scale_shape_manual(values = c("square","circle"),labels = c("ethnic","Value"), guide = guide_legend(title = "Segregation")) + 
 scale_x_discrete(limits = seq(10,90 ,by = 10)) +
  facet_wrap(~ fraction_blue, nrow = 1) +
  ggtitle("Liberals minority") +
  theme_bw()

# Increase ethnic

We only look at the behavior of liberals, as conservatives have minimal consequence. Combining the two plots looked awful

```{r et_liberals, fig.cap="OK Effect of ethnic liberals majority vs minority on liberals", echo = FALSE}

# etlib_maj <- df_etlib %>% filter(fraction_blue == 50 | fraction_blue == 80) %>% filter(eth_con_loc == 20 & eth_con_min == 20) %>% filter(val_con_loc == 0 & val_con_min == 0) %>% filter(eth_lib_min == 0)

etlib_maj <- df_sec %>% filter(fraction_blue == 50 | fraction_blue == 80)  %>% gather(key = subgroup, value = Clustetmj, de_cl_bl,dv_cl_bl,de_cl_or,dv_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_cl_bl","de_cl_or"), "Value" = c("dv_cl_bl","dv_cl_or") ),"Ethnic"),
              `ethnicity` = fct_relevel(fct_collapse(subgroup,"Liberals Majority" = c("de_cl_bl","dv_cl_bl"), "Liberals Minority" = c("de_cl_or","dv_cl_or")), "Liberals Majority")) # %>% filter(eth_lib_min == 0)

# data_maj = etlib_maj[which(etlib_maj$ID == "etlib_loc" & etlib_maj$eth_lib_min == 0),]

libmaj <-  ggplot(data =  etlib_maj[which(etlib_maj$ID == "etlib_loc" & etlib_maj$eth_lib_min == 0 & etlib_maj$eth_con_loc == 20  & etlib_maj$eth_con_min == 20 & etlib_maj$val_con_loc ==0 & etlib_maj$val_con_min == 0),], aes(x= eth_lib_loc,y = Clustetmj,linetype= as.factor(fraction_blue), shape =`segregation`,color = `ethnicity`) ) +
  geom_point(size=2) + geom_line() +
  facet_wrap(~`ethnicity`, dir = "v") +
   scale_color_manual(values = c("blue","orange"), name = "Ethnicity") +
  scale_shape_manual(values = c("square","circle"), name = "Segregation") +
   scale_linetype_manual(values = c("solid","dashed"), labels = c("50%","80%"), name = "% Majority") +
  xlab("ß ethnic liberals majority") +
  ylab("Spatial Clustering") +
  labs(caption = "ß ethnic liberals minority = 0") + theme_bw() +
  guides(color = FALSE) +
  theme(plot.caption = element_text(hjust = 0.5))

libmin <-  ggplot(data = etlib_maj[which(etlib_maj$ID == "etlib_min" & etlib_maj$eth_lib_loc == 0 & etlib_maj$eth_con_loc == 20  & etlib_maj$eth_con_min == 20 & etlib_maj$val_con_loc ==0 & etlib_maj$val_con_min == 0),], aes(x= eth_lib_min,y = Clustetmj,linetype= as.factor(fraction_blue), shape =`segregation`,color = `ethnicity`) ) + 
  geom_point(size=2) + geom_line() + 
  facet_wrap(~`ethnicity`, dir = "v") +
   scale_color_manual(values = c("blue","orange"), name = "Ethnicity") + 
  scale_shape_manual(values = c("square","circle"), name = "Segregation") + 
   scale_linetype_manual(values = c("solid","dashed"), labels = c("50%","80%"), name = "% Majority") +
  xlab("ß ethnic liberals minority") +
  ylab("Spatial Clustering") +
  labs(caption = "ß ethnic liberals majority = 0") + theme_bw() +
  guides(color = FALSE) +
  theme(plot.caption = element_text(hjust = 0.5))

ggpubr::ggarrange(libmaj,libmin, common.legend = TRUE, legend = "bottom")

# high randomness

# libmaj_h <-  ggplot(data =  etlib_maj[which(etlib_maj$ID == "etlib_loc" & etlib_maj$eth_lib_min == 0 & etlib_maj$eth_con_loc == 5  & etlib_maj$eth_con_min == 5 & etlib_maj$val_con_loc ==0 & etlib_maj$val_con_min == 0),], aes(x= eth_lib_loc,y = Clustetmj,linetype= as.factor(fraction_blue), shape =`segregation`,color = `ethnicity`) ) +
#   geom_point(size=2) + geom_line() +
#   facet_wrap(~`ethnicity`, dir = "v") +
#    scale_color_manual(values = c("blue","orange"), name = "Ethnicity") +
#   scale_shape_manual(values = c("square","circle"), name = "Segregation") +
#    scale_linetype_manual(values = c("solid","dashed"), labels = c("50%","80%"), name = "% Majority") +
#   xlab("ß ethnic liberals majority") +
#   ylab("Spatial Clustering") +
#   labs(caption = "ß ethnic liberals minority = 0") + theme_bw() +
#   guides(color = FALSE) +
#   theme(plot.caption = element_text(hjust = 0.5))
# 
# libmin_h <-  ggplot(data = etlib_maj[which(etlib_maj$ID == "etlib_min" & etlib_maj$eth_lib_loc == 0 & etlib_maj$eth_con_loc == 5  & etlib_maj$eth_con_min == 5 & etlib_maj$val_con_loc ==0 & etlib_maj$val_con_min == 0),], aes(x= eth_lib_min,y = Clustetmj,linetype= as.factor(fraction_blue), shape =`segregation`,color = `ethnicity`) ) + 
#   geom_point(size=2) + geom_line() + 
#   facet_wrap(~`ethnicity`, dir = "v") +
#    scale_color_manual(values = c("blue","orange"), name = "Ethnicity") + 
#   scale_shape_manual(values = c("square","circle"), name = "Segregation") + 
#    scale_linetype_manual(values = c("solid","dashed"), labels = c("50%","80%"), name = "% Majority") +
#   xlab("ß ethnic liberals minority") +
#   ylab("Spatial Clustering") +
#   labs(caption = "ß ethnic liberals majority = 0") + theme_bw() +
#   guides(color = FALSE) +
#   theme(plot.caption = element_text(hjust = 0.5))
# 
# 
# ggpubr::ggarrange(libmaj_h,libmin_h, common.legend = TRUE, legend = "bottom")

```{r Ethnic liberals, fig.cap="Each grouptype, distribution liberals faceted by ethnic ratio", echo = FALSE}

df_fin <- df_3D %>% mutate(RND = case_when(
  val_lib_loc==5 & val_lib_min==5 & eth_con_loc == 5 & eth_con_min == 5 ~ "H",
  val_lib_loc==20 & val_lib_min==20 & eth_con_loc == 20 & eth_con_min == 20 ~ "L"
))

subset(df_fin, eth_lib_loc != 0 & eth_lib_min != 0) %>% gather(subgroup, Segra, de_sq_bl,dv_sq_bl) %>% ggplot(aes(x=circle_orange,y=Segra,shape = subgroup, color = RND)) + geom_point() + geom_line() +
  scale_color_manual(values = c("green","purple"),labels = c("high","low"), guide = guide_legend(title = "Randomness")) + 
  scale_shape_manual(values = c("square","circle"),labels = c("ethnic","Value"), guide = guide_legend(title = "Segregation")) + 
 scale_x_discrete(limits = seq(10,90 ,by = 10)) +
  facet_wrap(~ fraction_blue, nrow = 1) +
  ggtitle("Conservative majority") +
  theme_bw()

subset(df_fin, eth_lib_loc != 0 & eth_lib_min != 0) %>% gather(subgroup, Segra, de_cl_bl,dv_cl_bl) %>% ggplot(aes(x=circle_orange,y=Segra,shape = subgroup, color = RND)) + geom_point() + geom_line() +
  scale_color_manual(values = c("green","purple"),labels = c("high","low"), guide = guide_legend(title = "Randomness")) + 
  scale_shape_manual(values = c("square","circle"),labels = c("ethnic","Value"), guide = guide_legend(title = "Segregation")) + 
 scale_x_discrete(limits = seq(10,90 ,by = 10)) +
  facet_wrap(~ fraction_blue, nrow = 1) +
  ggtitle("Liberals majority") +
  theme_bw()

subset(df_fin, eth_lib_loc != 0 & eth_lib_min != 0)  %>% gather(subgroup, Segra, de_sq_or,dv_sq_or) %>% ggplot(aes(x=circle_orange,y=Segra,shape = subgroup, color = RND)) + geom_point() + geom_line() +
  scale_color_manual(values = c("green","purple"),labels = c("high","low"), guide = guide_legend(title = "Randomness")) + 
  scale_shape_manual(values = c("square","circle"),labels = c("ethnic","Value"), guide = guide_legend(title = "Segregation")) + 
 scale_x_discrete(limits = seq(10,90 ,by = 10)) +
  facet_wrap(~ fraction_blue, nrow = 1) +
  ggtitle("Conservative minority") +
  theme_bw()

subset(df_fin, eth_lib_loc != 0 & eth_lib_min != 0) %>% gather(subgroup, Segra, de_cl_or,dv_cl_or) %>% ggplot(aes(x=circle_orange,y=Segra,shape = subgroup, color = RND)) + geom_point() + geom_line() +
  scale_color_manual(values = c("green","purple"),labels = c("high","low"), guide = guide_legend(title = "Randomness")) + 
  scale_shape_manual(values = c("square","circle"),labels = c("ethnic","Value"), guide = guide_legend(title = "Segregation")) + 
 scale_x_discrete(limits = seq(10,90 ,by = 10)) +
  facet_wrap(~ fraction_blue, nrow = 1) +
  ggtitle("Liberals minority") +
  theme_bw()

```{r Ethnic liberalsT, fig.cap="Each grouptype, distribution liberals faceted by ethnic ratio", echo = FALSE}

df_fin <- df_3D %>% mutate(RND = case_when(
  val_lib_loc==5 & val_lib_min==5 & eth_con_loc == 5 & eth_con_min == 5 ~ "H",
  val_lib_loc==20 & val_lib_min==20 & eth_con_loc == 20 & eth_con_min == 20 ~ "L"
))

sb <- list(
  as.data.frame(cbind((subset(df_fin, eth_lib_loc != 0 & eth_lib_min != 0) %>% gather(subgroup, Segra, de_sq_bl,dv_sq_bl)),t="Conservative Majority")),
           as.data.frame(cbind((subset(df_fin, eth_lib_loc != 0 & eth_lib_min != 0) %>% gather(subgroup, Segra, de_cl_bl,dv_cl_bl)),t="Liberal Majority")),
            as.data.frame(cbind((subset(df_fin, eth_lib_loc != 0 & eth_lib_min != 0)  %>% gather(subgroup, Segra, de_sq_or,dv_sq_or)),t="Conservative Minority")),
           as.data.frame(cbind((subset(df_fin, eth_lib_loc != 0 & eth_lib_min != 0) %>% gather(subgroup, Segra, de_cl_or,dv_cl_or)),t="Liberal Minority"))
           )

for (i in sb) {

pl <-  ggplot(i, aes(x=circle_orange,y=Segra,shape = subgroup, color = RND)) + geom_point() + geom_line() +
  scale_color_manual(values = c("green","purple"),labels = c("high","low"), guide = guide_legend(title = "Randomness")) + 
  scale_shape_manual(values = c("square","circle"),labels = c("ethnic","Value"), guide = guide_legend(title = "Segregation")) + 
 scale_x_discrete(limits = seq(10,90 ,by = 10)) +
  facet_wrap(~ fraction_blue, nrow = 1) +
 ggtitle(i$t) +
  theme_bw()

plot(pl)

}

```{r 3Dsec, fig.cap="Increase ethnic preference, 3D", echo = FALSE}

sec_3D_high <- df_3D %>% filter(val_lib_loc==5,val_lib_min==5,eth_con_loc == 5,eth_con_min == 5,eth_lib_loc ==5,eth_lib_min==5) 
sec_3D_low <- df_3D %>% filter(val_lib_loc==20,val_lib_min==20,eth_con_loc == 20,eth_con_min == 20,eth_lib_loc ==20,eth_lib_min==20)

D3_e <- {
lowE_e <- plot_ly(sec_3D_high)  %>%
  add_trace(x= xx,y= yy,z=zz,
            scene = "scene1",
            type="scatter3d",
             mode="markers",
             marker = list(
             colorscale = "Reds",
             color= cols, showscale =  T,
             colorbar=list(title = "Ethnic \nExposure" ,x = -0.1,  len = 0.5, yanchor='bottom'))

 lowV_e<- plot_ly(sec_3D_high)  %>%   add_trace(x=xx,y=yy,z=zzv,
             scene =  "scene2",
             type="scatter3d",
             mode="markers", 
             marker = list( 
             colorscale = "Blues",
             color= colsv , showscale = T, reversescale=T,
             colorbar=list(title = "Value  \nExposure", len=0.5, yanchor='bottom'))
            )  %>% 
       layout(showlegend = F,
         "scene2" = list(
      xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
      yaxis = list(title = "% Liberal Minority"  ,autorange = "reversed"),
      zaxis = list(title = "Value Cluster")))

highE_e <- plot_ly(sec_3D_low)  %>%
  add_trace(x=xx,y=yy,z=zz,
            scene = "scene3",
            type="scatter3d",
             mode="markers",
             marker = list(
             colorscale = "Reds",
             color= cols, showscale =  T,
             colorbar=list(title = "Ethnic \nExposure" ,x = -0.1,  len = 0.5, yanchor='top'))

 highV_e<- plot_ly(sec_3D_low)  %>%   
    add_trace(x=xx,y=yy,z=zz,
     scene =  "scene4",
     type="scatter3d",
     mode="markers", 
     marker = list( 
     colorscale = "Blues",
     color= colsv , showscale = T, reversescale=T,
      colorbar=list(title = "Value  \nExposure", len=0.5, yanchor='top'))
            )  %>% 
       layout(showlegend = F,
         "scene4" = list(
      xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
      yaxis = list(title = "% Liberal Minority"   ,autorange = "reversed"),
      zaxis = list(title = "Value Cluster")))

subplot(lowE_e, lowV_e,  highE_e, highV_e) %>%

### Annex

@@

lib_cons_et <- ggpubr::ggarrange(cons_maj_et,cons_min_et, common.legend = TRUE, legend = "bottom")
lib_cons_et
#ggsave("lib_cons.jpg",plot=lib_cons)

ggpubr::annotate_figure(lib_cons_et,top = "Effect of liberals majority vs minority on ethnic segregation conservatives")

@@

```{r et_liberals_con, fig.cap="OK Effect of ethnic liberals majority vs minority on liberals", echo = FALSE}

# etlib_maj <- df_etlib %>% filter(fraction_blue == 50 | fraction_blue == 80) %>% filter(eth_con_loc == 20 & eth_con_min == 20) %>% filter(val_con_loc == 0 & val_con_min == 0) %>% filter(eth_lib_min == 0)

etlib_maj <- df_sec %>% filter(fraction_blue == 50 | fraction_blue == 80)  %>% gather(key = subgroup, value = Clustetmj, de_sq_bl,dv_sq_bl,de_sq_or,dv_sq_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_bl","de_sq_or"), "Value" = c("dv_sq_bl","dv_sq_or") ),"Ethnic"),
              `ethnicity` = fct_relevel(fct_collapse(subgroup,"Liberals Majority" = c("de_sq_bl","dv_sq_bl"), "Liberals Minority" = c("de_sq_or","dv_sq_or")), "Liberals Majority")) # %>% filter(eth_lib_min == 0)

# data_maj = etlib_maj[which(etlib_maj$ID == "etlib_loc" & etlib_maj$eth_lib_min == 0),]

libmaj <-  ggplot(data =  etlib_maj[which(etlib_maj$ID == "etlib_loc" & etlib_maj$eth_lib_min == 0 & etlib_maj$eth_con_loc == 20  & etlib_maj$eth_con_min == 20 & etlib_maj$val_con_loc ==0 & etlib_maj$val_con_min == 0),], aes(x= eth_lib_loc,y = Clustetmj,linetype= as.factor(fraction_blue), shape =`segregation`,color = `ethnicity`) ) +
  geom_point(size=2) + geom_line() +
  facet_wrap(~`ethnicity`, dir = "v") +
   scale_color_manual(values = c("blue","orange"), name = "Ethnicity") +
  scale_shape_manual(values = c("square","circle"), name = "Segregation") +
   scale_linetype_manual(values = c("solid","dashed"), labels = c("50%","80%"), name = "% Majority") +
  xlab("ß ethnic liberals majority") +
  ylab("Spatial Clustering") +
  labs(caption = "ß ethnic liberals minority = 0") + theme_bw() +
  guides(color = FALSE) +
  theme(plot.caption = element_text(hjust = 0.5))

libmin <-  ggplot(data = etlib_maj[which(etlib_maj$ID == "etlib_min" & etlib_maj$eth_lib_loc == 0 & etlib_maj$eth_con_loc == 20  & etlib_maj$eth_con_min == 20 & etlib_maj$val_con_loc ==0 & etlib_maj$val_con_min == 0),], aes(x= eth_lib_min,y = Clustetmj,linetype= as.factor(fraction_blue), shape =`segregation`,color = `ethnicity`) ) + 
  geom_point(size=2) + geom_line() + 
  facet_wrap(~`ethnicity`, dir = "v") +
   scale_color_manual(values = c("blue","orange"), name = "Ethnicity") + 
  scale_shape_manual(values = c("square","circle"), name = "Segregation") + 
   scale_linetype_manual(values = c("solid","dashed"), labels = c("50%","80%"), name = "% Majority") +
  xlab("ß ethnic liberals minority") +
  ylab("Spatial Clustering") +
  labs(caption = "ß ethnic liberals majority = 0") + theme_bw() +
  guides(color = FALSE) +
  theme(plot.caption = element_text(hjust = 0.5))

ggpubr::ggarrange(libmaj,libmin, common.legend = TRUE, legend = "bottom")

# high randomness

# libmaj_h <-  ggplot(data =  etlib_maj[which(etlib_maj$ID == "etlib_loc" & etlib_maj$eth_lib_min == 0 & etlib_maj$eth_con_loc == 5  & etlib_maj$eth_con_min == 5 & etlib_maj$val_con_loc ==0 & etlib_maj$val_con_min == 0),], aes(x= eth_lib_loc,y = Clustetmj,linetype= as.factor(fraction_blue), shape =`segregation`,color = `ethnicity`) ) +
#   geom_point(size=2) + geom_line() +
#   facet_wrap(~`ethnicity`, dir = "v") +
#    scale_color_manual(values = c("blue","orange"), name = "Ethnicity") +
#   scale_shape_manual(values = c("square","circle"), name = "Segregation") +
#    scale_linetype_manual(values = c("solid","dashed"), labels = c("50%","80%"), name = "% Majority") +
#   xlab("ß ethnic liberals majority") +
#   ylab("Spatial Clustering") +
#   labs(caption = "ß ethnic liberals minority = 0") + theme_bw() +
#   guides(color = FALSE) +
#   theme(plot.caption = element_text(hjust = 0.5))
# 
# libmin_h <-  ggplot(data = etlib_maj[which(etlib_maj$ID == "etlib_min" & etlib_maj$eth_lib_loc == 0 & etlib_maj$eth_con_loc == 5  & etlib_maj$eth_con_min == 5 & etlib_maj$val_con_loc ==0 & etlib_maj$val_con_min == 0),], aes(x= eth_lib_min,y = Clustetmj,linetype= as.factor(fraction_blue), shape =`segregation`,color = `ethnicity`) ) + 
#   geom_point(size=2) + geom_line() + 
#   facet_wrap(~`ethnicity`, dir = "v") +
#    scale_color_manual(values = c("blue","orange"), name = "Ethnicity") + 
#   scale_shape_manual(values = c("square","circle"), name = "Segregation") + 
#    scale_linetype_manual(values = c("solid","dashed"), labels = c("50%","80%"), name = "% Majority") +
#   xlab("ß ethnic liberals minority") +
#   ylab("Spatial Clustering") +
#   labs(caption = "ß ethnic liberals majority = 0") + theme_bw() +
#   guides(color = FALSE) +
#   theme(plot.caption = element_text(hjust = 0.5))
# 
# 
# ggpubr::ggarrange(libmaj_h,libmin_h, common.legend = TRUE, legend = "bottom")

@@

```{r sec_test, fig.cap="Keep it for annex: effect of liberals or conservatives secondary preference in low or high determinism", echo = FALSE}
